\subsection{Shapiro-Wilk}

The Shapiro-Wilk test for goodness of fit requires that all of the values
are unique. In order to use the Shapiro-Wilk test, we
cannot use the grades without perturbing them in order to make them unique.
In one view, the grades given by the judges are severely rounded to increments
of 0.5 from a continuum of performances by the pilots.

Two methods to perturb the grades are
\begin{itemize}
\item add values selected from a random uniform distribution between -2.5 and
2.5.
\item add values selected from a random normal distribution.
\end{itemize}

Applying a uniform distribution is the Smirnov transformation described
in \cite{lemkol}.
The method uniformly and
reliably perturbs the data within the range and has the advantage of
prior use in practice. A disadvantage is that the mean
of the perturbed values can end-up anywhere between -2.5 and 2.5 added to
the actual grade.

Using the random normal distribution ensures that the mean of the perturbed
values will remain close to the actual grade value. The disadvantage is that
we must choose a standard deviation for the random normal distribution.
The standard deviation must be such that the resulting perturbations are
extremely rarely, with very low probability, outside of the range -2.5 to
2.5.  A second, potential disadvantage is that this is a variation of the
Smirnov transformation that, so far as we know,
we are inventing for this study

We chose to use for standard deviation a value that approximates the
distribution of Bates \cite{Bates}. The Bates distribution has the
advantage of being distributed along a fixed interval around a mean, with
decreasing probability for values further from the mean.
A mean of zero and variance of $1/12n * 5$,
where n is the number of instances of the grade, when used
with the normal distribution, approximates the distribution of Bates between
-2.5 and 2.5.

We perturbed the grades using random values chosen from a normal distribution
with mean equal to zero and standard deviation equal to $\sqrt{5/12n}$.
Choosing a standard deviation dependent on the number of instances
of the grade causes the perturbations to remain closer to zero when there
are more instances of a grade and within the -2.5 to 2.5 range.
We report the p-value for the Shapiro-Wilk normality test after perturbing
the grades.
